\section{Introduction}
\label{sec:introduction}

Strategy (formerly MicroStrategy, rebranded February 2025) announced its first Bitcoin purchase in August 2020: 21,454 BTC for roughly \$250 million. What began as an unconventional treasury allocation has since grown into the most aggressively leveraged cryptocurrency position ever assembled by a public company. By January 2026, Strategy held 713,502 Bitcoin with a cost basis of approximately \$54.3 billion, acquired through a financing strategy that would make most CFOs nervous and most academics skeptical.\footnote{All figures as of late January 2026 unless otherwise noted. The company trades under the ticker MSTR on NASDAQ. I use ``Strategy'' and ``MSTR'' interchangeably throughout.}

The conventional story treats MSTR as a simple Bitcoin proxy, a way for equity investors to gain exposure without holding the asset directly. This framing misses the more interesting dynamics at play. MSTR isn't just holding Bitcoin; it has engineered a capital structure designed to amplify returns in both directions while extracting value through financial engineering that rewards certain stakeholders at the expense of others.

I document conditional feedback dynamics consistent with what George Soros termed market reflexivity. The hypothesized loop works as follows: elevated stock prices enable cheap equity issuance; cheap equity funds Bitcoin purchases; Bitcoin purchases increase net asset value; higher NAV supports the stock price. The cycle persists as long as three conditions hold: access to capital markets, elevated implied volatility, and stable or rising Bitcoin prices. When any of these constants fails, the flywheel breaks. The empirical question is whether MSTR's behavior exhibits patterns consistent with this mechanism, and under what conditions the feedback operates.

This thesis examines four questions:

\begin{enumerate}
    \item How has MicroStrategy's financing strategy created a self-reinforcing feedback loop between its stock price, volatility, and Bitcoin accumulation?
    \item What is the quantitative relationship between MSTR's NAV premium and subsequent capital raising?
    \item How do convertible bond arbitrageurs amplify the reflexivity mechanism, and what does this mean for different investor classes?
    \item Under what conditions does the flywheel break, and who bears the losses when it does?
\end{enumerate}

\subsection{Hypotheses}

\textbf{H1:} MicroStrategy's NAV premium exhibits a statistically significant positive relationship with subsequent Bitcoin purchases, consistent with reflexive feedback.

\textbf{H2:} The self-reinforcing loop requires three conditions to persist: continuous capital raising capability, elevated implied volatility, and rising or stable Bitcoin prices.

\textbf{H3:} Retail equity investors face asymmetric downside risk compared to convertible arbitrageurs, who extract value through gamma scalping while maintaining hedged positions.

\subsection{Contribution}

The existing literature treats reflexivity as a qualitative concept, applies Merton models to traditional corporate assets, and examines convertible arbitrage in isolation. This thesis integrates all three frameworks to analyze a structure that didn't exist before 2020.

I contribute in three ways. First, I document patterns consistent with reflexive capital formation at the firm level using an event study around capital raises. While \citet{soros1987alchemy} offers theoretical insight without mathematical specification, I test whether MSTR's behavior exhibits observable patterns consistent with reflexive dynamics. The evidence shows that Strategy systematically raises capital during elevated premium windows, and that the premium exhibits extreme persistence rather than mean-reversion. Second, I frame MSTR equity as a call option on Bitcoin and analyze the capital structure through breakeven prices and asset/debt ratios rather than Merton model outputs that assume away Bitcoin's defining characteristics. Third, I describe how convertible arbitrageurs extract value from the structure through gamma scalping while retail equity holders bear leveraged directional risk.

The remainder of this section reviews the relevant literature. Subsequent sections cover capital structure analysis, methodology, results, discussion with comparative evidence from other Digital Asset Treasury Companies (DATCOs), and conclusion.

\input{chapters/literature}
